\prefacesection{Acknowledgements}

This seminar is the result of my hard work, wherein I have been helped and supported by several persons and institutions directly and indirectly. Now it is time to acknowledge their contributions.

Foremost, I would like to express my sincere gratitude to my project guide, Asso/Asst. Prof. [Guide's Name], for his/her continuous encouragement, invaluable guidance, motivation, and enthusiasm throughout my seminar. I appreciate his/her sincere help in terms of patience, time, and ideas, which made my seminar experience stimulating and productive.

My sincere gratitude goes to Dr. Anand Hareendran S, Head of the Department during my course period (2016-2020). I would also like to thank the project coordinator, Asst. Prof. Jisha James, for critically assessing my work and providing valuable suggestions. I would like to acknowledge the management of Muthoot Institute of Technology and Science for providing academic support to complete my seminar.

In my daily work, I have been blessed with a friendly and cheerful group of fellow students. I am very thankful to all the members of S7 CSE.

I would like to express my sincere gratitude to the technical staff of [Laboratory Name(s)] and all the staff of the Computer Science and Engineering Department for providing a good environment.

Besides this, several people have knowingly and unknowingly helped me in the successful completion of this seminar. I express my sincere gratitude to all of them.

\vfill % This pushes the name to the bottom
\hfill % This aligns the name to the right
[Your Name]
