\begin{thebibliography}{00}
% Begins the bibliography environment. The parameter {00} sets the width for the references.
%
%
% Reference 1
\bibitem{b1} G. Lavanya and S. D. Pande, ``Enhancing real-time object detection with YOLO algorithm,'' \textit{EAI Endorsed Transactions on Internet of Things}, vol. 10, 2023.
% Cites the first reference with authors, title, journal name, volume, and year.
%
% Reference 2
\bibitem{b2} Z. J. Khow, Y. F. Tan, H. A. Karim, and H. A. A. Rashid, ``Improved YOLOv8 model for a comprehensive approach to object detection and distance estimation,'' \textit{IEEE Access}, vol. 12, pp. 1--10, 2024.
% Cites the second reference with authors, title, journal name, volume, page range, and year.
%
% Reference 3
\bibitem{b3} M. Majumder and C. Wilmot, ``Automated vehicle counting from pre-recorded video using You Only Look Once (YOLO) object detection model,'' \textit{Journal of Imaging}, vol. 9, p. 456, 2023.
% Cites the third reference with authors, title, journal name, volume, and page number.
%
% Reference 4
\bibitem{b4} V. K. Deshpande, R. Bhalerao, and M. Chaturvedi, ``Modified YOLO module for efficient object tracking,'' \textit{IEEE Latin America Transactions}, vol. 21, pp. 123--134, 2023.
% Cites the fourth reference with authors, title, journal name, volume, page range, and year.
%
% Reference 5
\bibitem{b5} J. Redmon, S. Divvala, R. Girshick, and A. Farhadi, ``You Only Look Once: Unified, real-time object detection,'' \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pp. 779--788, 2016.
% Cites the fifth reference with authors, title, conference name, page range, and year.
%
% Reference 6
\bibitem{b6} M. Hussain, ``YOLOv1 to v8: Unveiling each variant—a comprehensive review of YOLO,'' \textit{Journal of Artificial Intelligence Research}, vol. 18, pp. 123--145, 2024.
% Cites the sixth reference with the author's name, title, journal name, volume, page range, and year.
%
% Reference 7
\bibitem{b7} Q. Liu, H. Ye, S. Wang, and Z. Xu, “YOLOv8-CB: Dense Pedestrian Detection Algorithm Based on In-Vehicle Camera,” \textit{Electronics}, vol. 13, no. 1, p. 236, 2024.
% Cites the seventh reference with authors, title, journal name, volume, issue number, and page number.
%
%
\end{thebibliography}
% Ends the bibliography environment.
%
%